\pkg{cubble}: An \proglang{R} Package for Organizing and Wrangling Multivariate Spatio-temporal Data

### 2023-06-29 cubble.Rmd
Fixing key words to be homogeneous with main text

---
documentclass: jss
classoption: shortnames
author:
  - name: H. Sherry Zhang
    affiliation: Monash University
    address: 21 Chancellors Walk, Clayton VIC 3800 Australia
    email: \email{huize.zhang@monash.edu}
  - name: Dianne Cook
    affiliation: Monash University
    address: 21 Chancellors Walk, Clayton VIC 3800 Australia
    email: dicook@monash.edu
  - name: Ursula Laa
    affiliation: 'University of  Natural `\\`{=latex} Resources and Life Sciences \AND'
    address: Gregor-Mendel-Straße 33, 1180 Wien, Austria
    email:  ursula.laa@boku.ac.at
  - name: Nicolas Langrené
    affiliation: 'BNU-HKBU `\\`{=latex} United International College'
    address: 2000 Jintong Road, Tangjiawan, Zhuhai, Guangdong Province, China
    email: nicolaslangrene@uic.edu.cn
  - name: Patricia Menéndez
    affiliation: Monash University
    address: 21 Chancellors Walk, Clayton VIC 3800 Australia
    email:  patricia.menendez@monash.edu
title:
  formatted: "\\pkg{cubble}: An \\proglang{R} Package for Organizing and Wrangling Multivariate Spatio-temporal Data"
  # If you use tex in the formatted title, alsoge supply version without
  plain:     "cubble: An R Package for Organizing and Wrangling Multivariate Spatio-temporal Data"
  # For running headers, if needed
  # short:     "\\pkg{foo}: A Capitalized Title"
abstract: >
     Multivariate spatio-temporal data refers to multiple measurements taken across space and time. For many analyses, spatial and time components can be separately studied: for example, to explore the temporal trend of one variable for a single spatial location, or to model the spatial distribution of one variable at a given time. However for some studies, it is important to analyze different aspects of the spatio-temporal data simultaneously, like for instance, temporal trends of multiple variables across locations. In order to facilitate the study of different portions or combinations of spatio-temporal data, we introduce a new class, \code{cubble}, with a suite of functions enabling easy slicing and dicing on different spatio-temporal components.  The proposed \code{cubble} class ensures that all the components of the data are easy to access and manipulate while providing flexibility for data analysis. In addition, the \pkg{cubble} package facilitates visual and numerical explorations of the data while easing data wrangling and modelling. The \code{cubble} class and the tools implemented in the package are illustrated with different examples of Australian climate data.
keywords:
  # at least one keyword must be supplied
  formatted: [spatial, temporal, spatio temporal, "\\proglang{R}", environmental data, exploratory data analysis]
  plain:     [spatial, temporal, spatio temporal, R, environmental data, exploratory data analysis]
preamble: >
  \usepackage{amsmath}
  \usepackage{array}
output: 
  bookdown::pdf_book:
    base_format: rticles::jss_article
bibliography: references.bib
---

>>>>

---
documentclass: jss
classoption: shortnames
author:
  - name: H. Sherry Zhang
    affiliation: Monash University
    address: 21 Chancellors Walk, Clayton VIC 3800 Australia
    email: \email{huize.zhang@monash.edu}
  - name: Dianne Cook
    affiliation: Monash University
    address: 21 Chancellors Walk, Clayton VIC 3800 Australia
    email: dicook@monash.edu
  - name: Ursula Laa
    affiliation: 'University of  Natural `\\`{=latex} Resources and Life Sciences \AND'
    address: Gregor-Mendel-Straße 33, 1180 Wien, Austria
    email:  ursula.laa@boku.ac.at
  - name: Nicolas Langrené
    affiliation: 'BNU-HKBU `\\`{=latex} United International College'
    address: 2000 Jintong Road, Tangjiawan, Zhuhai, Guangdong Province, China
    email: nicolaslangrene@uic.edu.cn
  - name: Patricia Menéndez
    affiliation: Monash University
    address: 21 Chancellors Walk, Clayton VIC 3800 Australia
    email:  patricia.menendez@monash.edu
title:
  formatted: "\\pkg{cubble}: An \\proglang{R} Package for Organizing and Wrangling Multivariate Spatio-temporal Data"
  # If you use tex in the formatted title, alsoge supply version without
  plain:     "cubble: An R Package for Organizing and Wrangling Multivariate Spatio-temporal Data"
  # For running headers, if needed
  # short:     "\\pkg{foo}: A Capitalized Title"
abstract: >
     Multivariate spatio-temporal data refers to multiple measurements taken across space and time. For many analyses, spatial and time components can be separately studied: for example, to explore the temporal trend of one variable for a single spatial location, or to model the spatial distribution of one variable at a given time. However for some studies, it is important to analyze different aspects of the spatio-temporal data simultaneously, like for instance, temporal trends of multiple variables across locations. In order to facilitate the study of different portions or combinations of spatio-temporal data, we introduce a new class, \code{cubble}, with a suite of functions enabling easy slicing and dicing on different spatio-temporal components.  The proposed \code{cubble} class ensures that all the components of the data are easy to access and manipulate while providing flexibility for data analysis. In addition, the \pkg{cubble} package facilitates visual and numerical explorations of the data while easing data wrangling and modelling. The \code{cubble} class and the tools implemented in the package are illustrated with different examples of Australian climate data.
keywords:
  # at least one keyword must be supplied
  formatted: [spatial, temporal, spatio-temporal, "\\proglang{R}", environmental data, exploratory data analysis]
  plain:     [spatial, temporal, spatio-temporal, R, environmental data, exploratory data analysis]
preamble: >
  \usepackage{amsmath}
  \usepackage{array}
output: 
  bookdown::pdf_book:
    base_format: rticles::jss_article
bibliography: references.bib
---

### 2023-06-29 cubble.tex
Fixing key words to be homogeneous with main text

\Keywords{spatial, temporal, spatio temporal, \proglang{R}, environmental data, exploratory data analysis}
\Plainkeywords{spatial, temporal, spatio temporal, R, environmental data, exploratory data analysis}

>>>>

\Keywords{spatial, temporal, spatio-temporal, \proglang{R}, environmental data, exploratory data analysis}
\Plainkeywords{spatial, temporal, spatio-temporal, R, environmental data, exploratory data analysis}
